\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{listings}
\usepackage[colorlinks]{hyperref}
\usepackage{xspace}
\usepackage{multicol}
\usepackage{abstract}
\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}
\input{macros}

\begin{document}
\title{\Qed: proving in logic modulo}
\author{Loïc Correnson}
\twocolumn[
\maketitle

\begin{abstract}
  We propose a framework for manipulating in a efficient way terms and
  formul{\ae} in classical logic modulo equality. \Qed was firstly
  designed for the generation of proof obligations of a
  weakest-precondition engine for \C programs inside the \FramaC
  framework. Efficiency is obtained by on-the-fly strong normalization
  of terms and maximal sharing of sub-terms. Then, \Qed is equipped by
  an extensible simplification engine. Rewriting rules,
  abstract-interpretation over terms and decision procedures are
  experimented inside the simplification engine. We finally present
  both an automated and interactive theorem prover in logic modulo.
\end{abstract}
\vspace{1cm}
]

\section*{Introduction}

Automated theorem prover for classical logic is an extensive research
domain with very powerful operational results. Not all theorem provers
are efficient over the same class of properties, and it is interesting
to combine several theorem provers to achieve proof of complex
logic propositions.

\TODO

\input{qed-logic}
\input{qed-terms}
\input{qed-proof}

\end{document}
